---
title       : Car Evaluation Project
subtitle    : Project for Coursera Developing Data Products 
author      : Explorer 123, Dec 2014
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Project Introduction

This application takes desired attributes of the car, as user inputs and based on those inputs gives the  the number of cars and their acceptability in a bar plot. 

#### Input: 
Desired attributes of the car e.g. number of doors, safety Rating, maintenance cost etc.   

### Processing:
Selects the Acceptaility rating of cars and number of cars with that acceptability.   

#### Result:
Bar plot of number of cars(Y axis) with acceptability (X axis).     Acceptability values can be:  
unacc- Unacceptable   
acc - Acceptable  
good - Good  
vgood - Very Good  

**Data source for the project**: http://archive.ics.uci.edu/ml/machine-learning-databases/car/  



--- .class #id 

## R code 
Read data, filter data on attribute selections(e.g. below), get car evaluation results
```{r project_read, echo=TRUE, eval=TRUE, }
library(dplyr)
d1<-read.table("http://archive.ics.uci.edu/ml/machine-learning-databases/car/car.data", 
sep=",", header=FALSE)
colnames(d1)<-c("buyingprice","maintcost","doors","persons","lugboot","safety","car")
sub<-d1 %>%
select(car,buyingprice,maintcost,doors,persons,lugboot,safety) %>%
        filter(buyingprice=='med' & maintcost=='med' &
                doors %in% c('2','3') & persons %in% c('2','4') & 
                lugboot %in% c('big','med') & safety=='high')
agg<-aggregate(sub,by=list(sub$car),FUN=length)
agg
```

--- .class #id 
## Bar Plot
Bar plot shows number of Cars & their evaluations[see slide 2 for possible values for the car acceptability] based on the attributes[see previous slide] selected.

```{r barplot, fig.height=4, fig.align='center',echo=TRUE, eval=TRUE}
      
      barplot(agg$car,
              ylab="Number of  cars",
              xlab="Car Evaluaton",
              names.arg=agg$Group.1)
```


--- .class #id 

## Shiny Application
Try the Car Evaluation shiny application!

<iframe src="https://123explorer.shinyapps.io/datapr/"></iframe>
--- .class #id 




